The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Minor changes

The last option we describe for {\tt nu} is {\tt IsLocal}.  When {\tt IsLocal => false} (the default is {\tt true}), then {\tt nu} ignores the option {\tt ContainmentTest} and the input ideal {\tt I}, and instead computes
\[
\min_{J \in \mathfrak{m}-\Spec R} (\nu_I^J(p^e))
\]
This is done by instead of computing for which $n$ we have $I^{n} \subseteq J^{[p^e]}$ (or equivalently, $(I^n)^{[1/p^e]} \subseteq J$), it computes for which $n$ we have $(I^n)^{[1/p^e]}$ is a unit ideal.

@@

Consider a  $\mathbb{Q}$-Gorenstein ring $R$ of characteristic $p>0$, whose index not divisible by $p$.
Given a parameter $t \in \mathbb{Q}$ and an element $f$ of $R$, the command {\tt isFPT(t,f)} outputs {\tt true} if $t$ is the $F$-pure threshold of $f$, and {\tt false} otherwise.
Moreover, the function {\tt compareFPT} provides further information about the relationship between $t$ and the $F$-pure threshold of $f$; namely,
{\tt compareFPT(t, f)} returns {\tt-1} , {\tt 0}, {\tt 1} when $t$ is less than, equal to, or greater than, respectively, the $F$-pure threshold of $f$.  Setting the option {\tt IsLocal} to {\tt true} tells the function to consider the $F$-pure threshold at the origin.  The following example illustrates this functionality.

>>>>

The last option we describe for {\tt nu} is {\tt IsLocal}.  When the value of {\tt IsLocal} is set to false (the default is {\tt true}), then {\tt nu} ignores the option {\tt ContainmentTest} and the input ideal {\tt I}, and instead computes
\[
\min_{J \in \mathfrak{m}-\Spec R} (\nu_I^J(p^e))
\]
This is done by instead of computing for which $n$ we have $I^{n} \subseteq J^{[p^e]}$ (or equivalently, $(I^n)^{[1/p^e]} \subseteq J$), it computes for which $n$ we have $(I^n)^{[1/p^e]}$ is a unit ideal.

@@

Consider a  $\mathbb{Q}$-Gorenstein ring $R$ of characteristic $p>0$, whose index not divisible by $p$.
Given a parameter $t \in \mathbb{Q}$ and an element $f$ of $R$, the command {\tt isFPT(t,f)} outputs {\tt true} if $t$ is the $F$-pure threshold of $f$, and {\tt false} otherwise.
Moreover, the function {\tt compareFPT} provides further information about the relationship between $t$ and the $F$-pure threshold of $f$; namely,
{\tt compareFPT(t, f)} returns {\tt-1}, {\tt 0}, or {\tt 1} when $t$ is less than, equal to, or greater than, respectively, the $F$-pure threshold of $f$.  Setting the option {\tt IsLocal} to {\tt true} tells the function to consider the $F$-pure threshold at the origin.  The following example illustrates this functionality.
